Examples of functions

### 2024-08-22 README.Rmd
updating

The goal of criticalvalue is to ...

@@

``` r
# require(devtools)
devtools::install_github("psicostat/criticalESvalue")
```

## Installation (temporary)

The package is not production-ready thus to test the feature we suggest to clone or download the repository, open the R Project and load the functions with `devtools::load_all()`.

## Example from fitted objects

This is a basic example which shows you how to solve a common problem:

@@

```{r example}
# library(criticalvalue) # when the package will be ready
devtools::load_all() # loading all functions for testing

# t-test (welch)

@@

dat <- data.frame(x, y, z, q)
fit <- lm(y ~ x + q + z, data = dat)
fit <- critical(fit)
fit
summary(fit)

# linear model (standardized)
fit <- lm(y ~ x + q + z, data = dat)
fit <- critical(fit, standardize = TRUE)
fit
summary(fit)
```

@@

```{r}
require(metafor)
dat <- escalc(measure="RR", ai=tpos, bi=tneg, ci=cpos, di=cneg, data=dat.bcg)
fit <- rma(yi, vi, mods=cbind(ablat, year), data=dat)
critical(fit)
```

>>>>

The goal of criticalvalue is to ...
<!-- TODO aggiungi qualche riga qui -->

@@

``` r
# require(remotes)
remotes::install_github("psicostat/criticalESvalue")
```

## Examples

```{r}
# loading the package
library(criticalESvalue)
```

@@

```{r example}
# t-test (welch)

@@

dat <- data.frame(x, y, z, q)
fit <- lm(y ~ x + q + z, data = dat)
fit <- critical(fit)
fit
summary(fit)
```

@@

```{r}
library(metafor)
dat <- escalc(measure="RR", ai=tpos, bi=tneg, ci=cpos, di=cneg, data=dat.bcg)
fit <- rma(yi, vi, mods=cbind(ablat, year), data=dat)
critical(fit)
```
